\begin{rubric}{Employment History}
\entry*[May 2023 -- $\cdots\cdot$]%
	\textbf{Yandex,} Middle+ Software Engineer
        \par \textit{Junior (May 2023) $\rightarrow$ Middle (May 2024) $\rightarrow$ Middle+ (Aug 2025)}
        \par Internal platform for data engineers: deploy and operate Flink jobs/clusters.
        \par Stack: Flink, ZooKeeper, Spring Boot, PostgreSQL, jOOQ, Liquibase.
        \par\smallskip
        \textbf{Achievements:}
        \vspace{-0.5em}
        \begin{itemize} \itemsep -2pt
        \item Reduced Flink job startup time by \textbf{70\%} (in-service JobGraph compilation).
        \item Built CI/CD for clusters and jobs; implemented system for business-facing job metrics collection.
        \item Improved alerting, reduced noise; maintained connectors (YDB, ClickHouse, YT).
        \item Mentored an intern to a full-time role.
        \end{itemize}
%
% Blank lines result in extra space!
%
\entry*[December 2021 -- May 2023]%
	\textbf{Sber,} Junior Software Engineer
        \par Products for cash circulation support (cash collection forecasting). Migrated services to the internal cloud (OpenStack) and developed integration logic. Technologies: Git, Atlassian stack (Jira, Confluence, Bitbucket), Java, Spring.
%
\entry*[August 2021 -- December 2021]%
	\textbf{VBC,} Intern Java Developer
        \par Worked in a microservices architecture (Netflix stack): implemented complex business logic and optimized PostgreSQL interactions. Developed a flexible credit pricing service that accounts for company/individual history, bank rules, limits, and requirements.

\end{rubric}