\begin{rubric}{Employment History}
\entry*[May 2023 -- $\cdots\cdot$]%
	\textbf{Yandex,} Middle Software Engineer
        \par Yandex is one of the largest IT companies in Russia, developing widely-used software and products. Developing Java and Python applications for data engineers, adapting open-source and proprietary technologies to meet their needs. Tech stack: Apache Flink, Apache ZooKeeper, Spring Boot, jOOQ, Liquibase, PostgreSQL, and internal tools.

        \textbf{Key contributions:}
        \begin{itemize}
        \item \textbf{Flink deployment optimization:} Implemented JobGraph compilation within service (as opposed to using Flink CLI) with low-level Flink integration, reducing job startup time by 70\% average.
        \item \textbf{CI/CD:} Created various CI/CD pipelines for Flink clusters and jobs.
        \item \textbf{Observability:} Implemented a solution for flexible business metrics supply (job efficiency metrics from business perspective).
        \item \textbf{Operations:} Improved alerting organization, reduced noise, maintained connectors (YDB, ClickHouse, YT).
        \item \textbf{Knowledge sharing:} Mentored an intern to full-time position.
        \end{itemize}
%
% Blank lines result in extra space!
%
\entry*[December 2021 -- May 2023]%
	\textbf{Sber,} Junior Software Engineer
        \par Sber is one of the largest companies in Russia, primarily specializing in banking services. Improved business-critical products and implemented new features. Technologies: Git, Atlassian Stack (Jira, Confluence, Bitbucket), Java, and Spring.
%
\entry*[August 2021 -- December 2021]%
	\textbf{VBC,} Intern Java Developer
        \par VBC provides a financial marketplace and tools for tender participation. Worked with microservices architecture using the Netflix stack, implemented complex business logic, and optimized PostgreSQL database interactions. Developed a flexible credit pricing service that accounts for company/individual history, bank rules, limits, and requirements.

\end{rubric}